Prediction is Hard (Especially About the Future)

### 2015-08-07 Manuscript.tex
Updates from ShareLaTeX

\maketitle
\begin{abstract}
This paper provides ...  
\end{abstract}
\section{Introduction}
\section{Cluster and Contrast}
A recurring data analysis pattern in this paper is $cluster+contrast$. The data is distilled into a few clusters using a clustering scheme. Then lessons are inferred by studying the differences between these clusters. These lessons are used to generate rules that can be applied in any context.
\subsection{Clustering}
There are a wide variety of clustering methods to choose from. A study by Ganesan~\cite{div14} explored different clustering methods for software engineering data using the effort and defect data from the PROMISE repository~\cite{promise}. In that study methods such as K-Means, mini-batch-K-Means, DBScan, EM, Ward, and WHERE were investigated. The results of the study showed that the size and number of clusters is more important that the specifics of the techniques used.

For this purposes of this work, we have chosen WHERE, a clustering scheme which is capable of generating at least $\sqrt{N}$ clusters given $N$ instances. In addition to this, WHERE has been shown to run fast while ignoring spurious dimensions~\cite{menzies2013}. This is particularly useful, for much of the DE data is noisy, in that they contain a information not associated with the target variable. 
\subsection{Finding Contrasts}
All the following methods use clustering in the form of WHERE, a top-down clustering method which recursively splits the data in two along a dimension that represents the highest variability, shown as Step-1 in figure \ref{fig:xtrees_bare}. Several algorithms are explored as possible tools used to identify contrast between clusters these include Nearest Neighbors methods, Case Based Reasoning, and Decision Trees.

\subsubsection{Nearest Neighbors}
T
\subsubsection{Case Based Reasoning}

@@

\subsection{Assessment}
\section{Experiments}
\subsection{Data}
\subsection{When not to Plan?}
\subsection{Evaluation}
\subsection{Results}
\section{Threats to Validity}
\section{Conclusion}
\section*{Acknowledgements}
\bibliographystyle{plain}

>>>>

\maketitle
\begin{abstract}
This paper provides ...  
\end{abstract}
\section{Introduction}
\section{Cluster and Contrast}
A recurring data analysis pattern in this paper is $cluster+contrast$. The data is distilled into a few clusters using a clustering scheme. Then lessons are inferred by studying the differences between these clusters. These lessons are used to generate rules that can be applied in any context.
\subsection{Clustering}
There are a wide variety of clustering methods to choose from. A study by Ganesan~\cite{div14} explored different clustering methods for software engineering data using the effort and defect data from the PROMISE repository~\cite{promise}. In that study methods such as WHERE, K-Means, mini-batch-K-Means, DBScan, EM, and Ward were investigated. The results of the study showed that the size and number of clusters is more important that the specifics of the techniques used.

For this purposes of this work, we have chosen WHERE, a clustering scheme which is capable of generating at least $\sqrt{N}$ clusters given $N$ instances. In addition to this, WHERE has been shown to run fast while ignoring spurious dimensions~\cite{menzies2013}. This is particularly useful, for much of the SE data is noisy, they contain a information not associated with the target variable.

\subsection{Finding Contrasts}
All the following methods use clustering in the form of WHERE, a top-down clustering method which recursively splits the data in two along a dimension that represents the highest variability, shown as Step-1 in figure \ref{fig:xtrees_bare}. In this work we have explored several algorithms as possible tools used to identify contrast between clusters. These fall into three broad categories: a) Case Based Reasoning techniques (Nearest Neighbors), b) A Gradient base planner (called HOW), and c) Decision Trees.

\subsubsection{Case Based Reasoning}

Case-based reasoning seeks to find solutions to problems by emulating human recollection and adaptation from past experiences. It has found extensive usage in Artificial Intelligence because it offers several advantages. However, one of the most important benefits that CBR has to offer is that it works on a ``case-by-case'' basis. Therefore it's advise is tailored to be specific to the particular case being considered. Several paper in SE have applied this technique, most of all for effort estimation ~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use}.

A classic example of a CBR is a nearest neighbor approach. The nearest neighbor approach is rather straight forward and has been developed as a "straw-man"; i.e., a simple baseline tool to act as a benchmark used to evaluate other methods.

Our approach is rather straight forward, in that we divide the $N$ training samples into $\sqrt{N}$ clusters and compute the centroid of these clusters. For every test case, we identify a cluster from the training set that most closely resembles it. Following this, we find the nearest cluster with a better performance score. The differences in the attributes between these two clusters constitute the \textit{"contrast set"}. These contrast sets acts as plans that can be used to reflect over the test cases to improve them.

In most SE applications, not all features contribute equally to a problem. With this in mind, we opine that it would be beneficial if the above method is extended to include some form of feature weighting, thus enabling the tools to recommend changes to only the most informative features.

\subsubsection{HOW}

HOW is a very different planner to other CBR systems. HOW

@@

\subsection{Assessment}
\section{Experiments}
\subsection{Data}

\begin{figure*}[!t]
\scriptsize
   \begin{center}
   \begin{minipage}{.46\linewidth}
    \begin{tabular}{r@{~}|l@{~}|r@{~}|l@{~}|r@{~}|r@{~}|} \cline{2-6}
   & \multicolumn{5}{c|}{ }\\

   & \multicolumn{5}{c|}{ Data set  properties}\\ 
   & \multicolumn{5}{c|}{  }\\ 
           & \multicolumn{2}{c|}{training}   & \multicolumn{3}{c|}{testing}      \\ \cline{2-6}
   data set      & versions           & cases & versions     & cases    & \% defective             \\ \hline
        jedit    & 3.2, 4.0, 4.1, 4.2 & 1257      & 4.3          & 492          & 2 \\
        ivy      & 1.1, 1.4           & 352       & 2.0          & 352          & 11 \\
        camel    & 1.0, 1.2, 1.4      & 1819      & 1.6          & 965          & 19 \\
        ant      & 1.3, 1.4, 1.5, 1.6 & 947       & 1.7          & 745          & 22 \\
        synapse  & 1.0, 1.1           & 379       & 1.2          & 256          & 34 \\
        velocity & 1.4, 1.5           & 410       & 1.6          & 229          & 34 \\
        lucene   & 2.0, 2.2           & 442       & 2.4          & 340          & 59 \\
        poi      & 1.5, 2, 2.5        & 936       & 3.0          & 442          & 64 \\
        xerces   & 1.0, 1.2, 1.3      & 1055      & 1.4          & 588          & 74  \\ 
        log4j    & 1.0, 1.1           & 244       & 1.2          & 205          & 92   \\
        xalan    & 2.4, 2.5, 2.6      & 2411      & 2.7          & 909          & 99  \\\hline

    \end{tabular}\end{minipage}\begin{minipage}{.4\linewidth}
    \begin{tabular}{|rrr|rrr|rr|l} \cline{1-8}
      \multicolumn{8}{|c|}{  }\\
      \multicolumn{8}{|c|}{  Results from learning}\\
       \multicolumn{8}{|c|}{   }\\
   \multicolumn{3}{|c|}{untuned} & \multicolumn{3}{c|}{tuned} & \multicolumn{2}{c|}{change}\\
  \cline{1-8}

  pd & pf & good? & pd & pf & good? & pd & pf\\\cline{1-8}
  55 & 29 &   & 64 & 29 & y & 9 & 0&$\star$\\
  65 & 35 & y & 65 & 28 & y & 0 & -7&$\star$\\
  49 & 31 &   & 56 & 37 &   & 5 & 6\\
  49 & 13 & y & 63 & 16 & y & 14 & 3&$\star$\\
  45 & 19 &   & 47 & 15 &   & 2 & -4\\
  78 & 60 &   & 76 & 60 &   & -2 & 0\\
  56 & 25 &   & 60 & 25 & y & 4 & 0\\
  56 & 31 &   & 60 & 10 & y & 4 & -21&$\star$\\
 30 & 31 &   & 40 & 29 &   & 10 & -2&$\times$\\
  32 & 6 &   & 30 & 6 &   & -2 & 0&$\times$\\
  38 & 9 &   & 47 & 9 &   & 9 & 0&$\times$\\
\hline 
\end{tabular}

\end{minipage}
\end{center}

    \caption{Training and test {\em data set properties} for the Jureczko data sets,
    sorted in ascending order of \% defective examples.
    On the right-hand-side, we show the {\em results from learning}.
    Data is ``good'' if it has recall over 60\% and false alarm under 40\%
(and note that, after tuning, there are more ``good'' than before).
Data   marked with ``$\star$'' show large improvements in performance, after tuning.
Data   marked with ``$\times$'' are ``not good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
}\label{fig:j}
\end{figure*}
\subsection{When not to Plan?}
\subsection{Evaluation}
\subsection{Results}
\section{Threats to Validity}
\section{Conclusion}
\section*{Acknowledgements}
\bibliographystyle{plain}
